Comments on Latent Ranking

### 2021-06-25 output_scripts/revisions_may.Rmd
update to also plot p values, try design better simulation study

all_ks_p %>% 
  filter(ks != 0) %>% 
  mutate(log_p = -log(ks)) %>% 
  ggplot(aes(log_p)) + 
  geom_histogram(aes(fill = Method)) +
  scale_fill_manual(values = cols_plot) +
  labs(y = "Negative Log KS Statistic P Value") +
  facet_wrap(~Method)

>>>>

all_ks_p %>% ggplot(aes(Method, ks)) +
  geom_boxplot(aes(fill = Method)) +
  scale_fill_manual(values = cols_plot) +
  labs(y = "P Value", title = "All Simulations")

all_ks_p %>% 
  filter(ks != 0) %>% 
  # mutate(log_p = -log(ks)) %>% 
  ggplot(aes(log_p)) + 
  geom_histogram(aes(fill = Method)) +
  scale_fill_manual(values = cols_plot) +
  labs(y = "Negative Log KS Statistic P Value") +
  facet_wrap(~Method)

### repeat for 1 simulation
sims <- 12
m1_ks_p <- tibble(Method = "C-HP",
       ks = as.vector(KS_p_model1_array[sims, ,]))

all_ks_p %>% ggplot(aes(Method, ks)) +
  geom_boxplot(aes(fill = Method)) +
  scale_fill_manual(values = cols_plot) +
  labs(y = "P Value", title = "single simulation")
